### 2022-02-18 sections/systematic_uncertainties.tex
major update v1.0

Another significant background in hadronic channel stems from the $Z\rightarrow \tau\tau$ samples, several sources of uncertainty are
considered for these samples: the PDF variation considering the standard deviation of the 100 NNPDF replicas event weights of NNPDF3.0nnlo PDF
set used in Sherpa, renormalisation ($\mu_{R}$) and factorisation scales ($\mu_{F}$), jet-to-parton matching uncertainty, resummation scale uncertainty,
variation in the choice of $\alpha_{S}$, alternative PDF variation evaluated comparing predictions from NNPDF3.0nnlo PDF set (nominal)
with MMHT2014nnlo68cl and CT14nnlo PDF sets.

@@

The statistical uncertainties of the fake $\had$ background calibration in the leptonic channel is applied with uncorrelated uncertainties for different fake $\had$ source and different $\pt$ slices. The uncertainties of the ABCD method is applied with a normalisation factor for muon and electron respectively considering both statistical fluctuation and the differences between signal regions.

The uncertainties of the fake factor method applied in hadronic channel includes statistical uncertainties of each fake factor and different sets of fake factors derived from different signal depleted CRs.

@@

Several normalisation and shape uncertainties are taken into account for the $\Hq$ and $pp\to tH$ signals.
Uncertainties of the Higgs boson branching ratios are taken into account
following the recommendation in Ref.~\cite{deFlorian:2016spz}.
The uncertainty of ISR, FSR, scale and PDF are considered in all SRs. The parton shower uncertainties is estimated by comparing
the nominal to an alternative sample interfaced with {\herwig7}.
%the predictions from {\powheg} interfaced either to {\pythiaeight} or {\herwig7}. 
%treated correlatedly with $\ttbar$ samples.

\begin{table}[htbp]
\caption{List of relative uncertainties of the signal strength from the combined fit in hadronic channel. The uncertainties are symmetrised for presentation and grouped into the categories described in the text. %The quadrature sum of the individual uncertainties is not equal to the total uncertainty due to correlations introduced by the fit
}
\small
\centering
\begin{tabular}{cc} \toprule\toprule
$\text{Uncertainty}    $   & $\Delta\mu/\mu[\%]$ \\\midrule
$\text{Fake modelling} $   & $13.5$ \\
$\text{Instrument}     $   & $2.6$  \\
$\text{Jets}           $   & $1.7$   \\
$\text{Met}            $   & $0.4$   \\
$\tau                  $   & $7.2$    \\
$\text{b-tagging}       $  & $0.3$    \\
$\text{Signal Theory}  $   & $1.5$   \\
$\text{Other MC theory} $  & $2.7$    \\
$t\bar{t} \text{theory}$  & $7.6$     \\\midrule
$\text{Statistics}      $  & $11.2$   \\
$\text{Total systematic}$  & $24.2$  \\ \midrule
$\text{Total}  $           & $26.7$ \\
\bottomrule\bottomrule
\end{tabular}
\label{tab:had_sys_impact}
\end{table}

\begin{table}[htbp]
\caption{List of relative uncertainties of the signal strength from the combined fit in leptonic channel. The uncertainties are symmetrised for presentation and grouped into  the categories described in the text. %The quadrature sum of the individual uncertainties is not equal to the total uncertainty due to correlations introduced by the fit
}
\small
\centering
\begin{tabular}{cc} \toprule\toprule
$\text{Uncertainty}        $ & $  \Delta\mu/\mu[\%]  $\\\midrule
$\text{Fake modelling}     $ & $       2.1             $\\
$\text{Instrument}         $ & $       0.7             $\\
$\text{Jets}               $ & $       2.8             $\\
$\text{Met}                $ & $       1.2             $\\
$\text{Lepton}             $ & $       0.7             $\\
$\tau                      $ & $       2.3             $\\
$\text{b-tagging}          $ & $       4.8             $\\
$\text{Signal Theory}      $ & $       6.9             $\\
$\text{Other MC theory}    $ & $       2.1             $\\
$t\bar{t} \text{theory}    $ & $       3.7             $\\\midrule
$\text{Statistics}         $ & $       5.9             $\\
$\text{Total systematic}   $ & $       12.9            $\\\midrule
$\text{Total}              $ & $       14.2            $\\
\bottomrule\bottomrule
\end{tabular}
\label{tab:lep_sys_impact}
\end{table}

>>>>

Another significant background in hadronic channel stems from the $Z\rightarrow \tau\tau$ samples, several sources of uncertainty are
considered for these samples: the PDF variation considering the standard deviation of the 100 NNPDF replicas event weights
of NNPDF3.0nnlo~\cite{Ball:2015NNPDF} PDF
set used in Sherpa, renormalisation ($\mu_{R}$) and factorisation scales ($\mu_{F}$), jet-to-parton matching uncertainty, resummation scale uncertainty,
variation in the choice of $\alpha_{S}$, alternative PDF variation evaluated comparing predictions from NNPDF3.0nnlo PDF set (nominal)
with MMHT2014nnlo68cl and CT14nnlo~\cite{Lai:2010vv,Gao:2013xoa} PDF sets.

@@

The statistical uncertainties on the fake $\had$ background calibration in the leptonic channel are applied with uncorrelated uncertainties for different fake $\had$ sources and
different $\pt$ slices. The uncertainty of the ABCD method is applied with a normalisation factor for muon and electron respectively considering both,
its statistical fluctuation and the differences between signal regions.
The uncertainties in the fake factor method applied in hadronic channel includes statistical uncertainties of each fake factor and different sets of fake factors derived from different signal depleted CRs.

@@

Several normalisation and shape uncertainties are taken into account for the $\Hq$ and $pp\to tH$ signals.
Uncertainties of the Higgs boson branching ratios are taken into account
following the recommendation in Ref.~\cite{deFlorian:2016spz}.
The uncertainty of ISR, FSR, scale and PDF are considered in all SRs. The parton shower uncertainties are estimated by comparing
the nominal to an alternative sample interfaced with {\herwig7}.
%the predictions from {\powheg} interfaced either to {\pythiaeight} or {\herwig7}. 
%treated correlatedly with $\ttbar$ samples.

\begin{table}[htbp]
\caption{List of relative uncertainties of the signal strength from the combined fit in the hadronic channels. The uncertainties are symmetrised for presentation and grouped into the categories described in the text. %The quadrature sum of the individual uncertainties is not equal to the total uncertainty due to correlations introduced by the fit
}
\small
\centering
\begin{tabular}{cc} \toprule\toprule
$\text{Uncertainty}    $   & $\Delta\mu/\mu[\%]$ \\\midrule
$\text{Fake modelling} $   & $13.5$ \\
$\text{Instrument}     $   & $2.6$  \\
$\text{Jets}           $   & $1.7$   \\
$\text{Met}            $   & $0.4$   \\
$\tau                  $   & $7.2$    \\
$\text{b-tagging}       $  & $0.3$    \\
$\text{Signal Theory}  $   & $1.5$   \\
$\text{Other MC theory} $  & $2.7$    \\
$t\bar{t} \text{theory}$  & $7.6$     \\\midrule
$\text{Statistics}      $  & $11.2$   \\
$\text{Total systematic}$  & $24.2$  \\ \midrule
$\text{Total}  $           & $26.7$ \\
\bottomrule\bottomrule
\end{tabular}
\label{tab:had_sys_impact}
\end{table}

\begin{table}[htbp]
\caption{List of relative uncertainties of the signal strength from the combined fit in the leptonic channels. The uncertainties are symmetrised for presentation and grouped into  the categories described in the text. %The quadrature sum of the individual uncertainties is not equal to the total uncertainty due to correlations introduced by the fit
}
\small
\centering
\begin{tabular}{cc} \toprule\toprule
$\text{Uncertainty}        $ & $  \Delta\mu/\mu[\%]  $\\\midrule
$\text{Fake modelling}     $ & $       2.1             $\\
$\text{Instrument}         $ & $       0.7             $\\
$\text{Jets}               $ & $       2.8             $\\
$\text{Met}                $ & $       1.2             $\\
$\text{Lepton}             $ & $       0.7             $\\
$\tau                      $ & $       2.3             $\\
$\text{b-tagging}          $ & $       4.8             $\\
$\text{Signal Theory}      $ & $       6.9             $\\
$\text{Other MC theory}    $ & $       2.1             $\\
$t\bar{t} \text{theory}    $ & $       3.7             $\\\midrule
$\text{Statistics}         $ & $       5.9             $\\
$\text{Total systematic}   $ & $       12.9            $\\\midrule
$\text{Total}              $ & $       14.2            $\\
\bottomrule\bottomrule
\end{tabular}
\label{tab:lep_sys_impact}
\end{table}
